### 2011-11-22 AffineLieAlgebras/Thesis/1.tex
More translations

We can use the Weyl character formula to obtain recurrent relations for weight multiplicities -- important tools for calculations \cite{il2010folded,kulish4sfa}.

For irreducible highest-weight modules recurrent relations have the following form
\begin{equation}
\label{eq:14}
m_{\xi }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
-\left( w(\rho )-\rho \right) }+\sum_{w\in W}\epsilon
(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.
\end{equation}
Formulae for Verma and generalized Verma modules differ only in the second term on the right-hand side. In case of Verma module it is just $\delta_{\xi,\mu}$. For generalized Verma module the summation in the second term on the right-hand side of \eqref{eq:14} is over the Weyl subgroup generated by reflections corresponding to roots $\{\alpha_{I}\}$.

Other recurrent formula can be obtained from a study of Casimir
elements action on irreducible highest weight modules
\cite{humphreys1997introduction}:
\begin{equation}
  \label{eq:15}
  m_{\lambda}=\frac{2}{(\mu+\rho)^{2}-(\lambda+\rho)^{2}}\sum_{\alpha\in \Delta^{+}}\sum_{k\geq 1} (\lambda+k\alpha,\alpha)m_{\lambda+k\alpha}.
\end{equation}
It is called the Freudenthal multiplicity formula.
Note that it is applicable only to irreducible modules.

We discuss the use of formulae \eqref{eq:14} and \eqref{eq:15} for computations in section \ref{sec:comp-algor}.

>>>>

Формула Вейля для характеров может быть использована для получения рекуррентных соотношений на кратности весов. Эти соотношения важны для вычислений \cite{il2010folded,kulish4sfa}.

Для неприводимых модулей старшего веса рекуррентные соотношения имеют вид
\begin{equation}
\label{eq:14}
m_{\xi }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
-\left( w(\rho )-\rho \right) }+\sum_{w\in W}\epsilon
(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.
\end{equation}
Формулы для модулей Верма и обобщенных модулей Верма отличаются только во вторым членом в правой части. В случае модулей Верма он равен $\delta_{\xi,\mu}$. Для обобщенного модуля Верма суммирование во втором члене в правой части равенства \eqref{eq:14} производится по элементам подгруппы Вейля порожденной отражениями, соответствующими корням $\{\alpha_{I}\}$.

В разделе \ref{subsec:Construct-recurrent-rel} мы покажем, что для модулей старшего веса эти соотношения могут быть получены как частный случай рекуррентных соотношений на коэффициенты ветвления.

Другая рекуррентная формула для кратностей может быть получена из рассмотрения действия элементов Казимира на неприводимых модулях старшего веса \cite{humphreys1997introduction}:
\begin{equation}
  \label{eq:15}
  m_{\lambda}=\frac{2}{(\mu+\rho)^{2}-(\lambda+\rho)^{2}}\sum_{\alpha\in \Delta^{+}}\sum_{k\geq 1} (\lambda+k\alpha,\alpha)m_{\lambda+k\alpha}.
\end{equation}
Эта формула называется формулой Фрейденталя. Заметим, что она применима только для неприводимых модулей

Применение рекуррентных соотношений \eqref{eq:14} и \eqref{eq:15} для вычисления кратностей весов обсуждается в разделе \ref{sec:comp-algor}.
